Deep Learning Project

### 2024-09-29 project/paper.tex
Fix typos and update CIFAR-10 performance table.
Corrected a typo in the TensorFlow dataset function and updated the table reference and accuracy values for CIFAR-10 models. Also adjusted access dates in the bibliography to reflect current information.

Training and validation sets were created in-situ using Tensorflow's \textt{image\_dataset\_from\_directory} function. The percentages were 80\% for training, and 20\% for validation.

@@

\subsubsection{Performance On CIFAR-10 Images}
The CIFAR-10 dataset consists of 1,000 32x32 RGB images (100 images per class). The accuracy of the two models against the unseen CIFAR-10 images is shown in \ref{tab:perf-unseen-imagenet}.

\begin{table}[ht]
    \centering
    \begin{tabular}{ll}
    \hline
    \textbf{Model} & \textbf{Accuracy} \\ \hline
    Simple & 21.4\% \\ \hline
    GoogLeNet Reproduction & ??? \\ \hline
    \end{tabular}
    \caption{Models' performance on unseen CIFAR-10 images}
    \label{tab:perf-unseen-imagenet}
\end{table}

The low accuracy of 21.4\% achieved by the simple model could be for several reasons. First, the models were trained on images having a relatively high resolution compared to CIFAR-10's 32x32 images. When models are trained on larger images, the models learn to identify fine-grained details which can become indistinguishable when down scaled to much smaller dimensions~\cite{simonyan2015vgg}.

>>>>

Training and validation sets were created in-situ using Tensorflow's \text{image\_dataset\_from\_directory} function. The percentages were 80\% for training, and 20\% for validation.

@@

\subsubsection{Performance On CIFAR-10 Images}
The CIFAR-10 dataset consists of 1,000 32x32 RGB images (100 images per class). The accuracy of the two models against the unseen CIFAR-10 images is shown in Table \ref{tab:perf-cifar10}.

\begin{table}[ht]
    \centering
    \begin{tabular}{ll}
    \hline
    \textbf{Model} & \textbf{Accuracy} \\ \hline
    Simple & 21.4\% \\ \hline
    GoogLeNet Reproduction & 22.6\% \\ \hline
    \end{tabular}
    \caption{Models' performance on unseen CIFAR-10 images}
    \label{tab:perf-cifar10}
\end{table}

The low accuracy of both models could be for several reasons. First, the models were trained on images having a relatively high resolution compared to CIFAR-10's 32x32 images. When models are trained on larger images, the models learn to identify fine-grained details which can become indistinguishable when down scaled to much smaller dimensions~\cite{simonyan2015vgg}.
